---
title: "Make Reduced From Partition"
author: "Steven Wolf"
date: "12/8/2020"
output: html_document
---

## Setup for the new function `make_reduced_from_partition`
Load all libraries and load the new function 

```{r}
library(concorR)
library(igraph)

source('mrfp.R')
```

## Proof of concept
I messed with `edge_betweenness` to find communities in the examples in the standard README for `concorR`.  They were not instructive (only one community), so I abandoned that.  Instead, I have created a random network and found communities there:
```{r}
set.seed(1234)
g  <-  erdos.renyi.game(50,p=0.2)
g_adj  <- as.matrix(as_adjacency_matrix(g))
ebc.g  <- edge.betweenness.community(g)
ebPart  <- list(ebc.g$membership)
```

First, let's show that the reduced network works for the degree statistic:
```{r}
g.red  <- make_reduced_from_partition(list(g_adj), ebPart, stat='degree')
plot_reduced(make_reduced_igraph(g.red$reduced_mat[[1]]))
```

And now, the density statistic:
```{r}
g.red.den  <- make_reduced_from_partition(list(g_adj), ebPart, stat='density')
plot_reduced(make_reduced_igraph(g.red.den$reduced_mat[[1]]))
```

## Full function text
```{r}
make_reduced_from_partition
```





